P versus NP

### 2019-12-26 doc/manuscript.tex
Fixed style doc

We also prove that $NL = NP$. There are several important consequences from this result, but we will only mention one of the principal outcomes, that is the Theorem Buhrman-Fortnow-van Melkebeek-Torenvliet \cite{BU00}. A set $A$ is auto-reducible if there exists an oracle polynomial time Turing machine $M$ such that $L(M^{A}) = A$ with the restriction that for all $x$, $M^{A}(x)$ does not query whether $x$ is in $A$ \cite{BU00}. When $NL = NP$, Buhrman, Fortnow, van Melkebeek and Torenvliet created a series of constructions to get an $A$ such that: $A$ is in $EXPSPACE$, $A$ is Turing-hard for $EXPSPACE$ and $A$ $``$diagonalizes$"$ against all possible auto-reductions \cite{BU00}.

>>>>

We also prove that $NL = NP$. There are several important consequences from this result, but we will only mention one of the principal outcomes, that is the Theorem Buhrman-Fortnow-van Melkebeek-Torenvliet \cite{BU00}. A set $A$ is auto-reducible if there exists an oracle polynomial time Turing machine $M$ such that $L(M^{A}) = A$ with the restriction that for all $x$, $M^{A}(x)$ does not query whether $x$ is in $A$ \cite{BU00}. When $NL = NP$, Buhrman, Fortnow, van Melkebeek and Torenvliet created a series of constructions to get an $A$ such that $A$ is in $EXPSPACE$, $A$ is Turing-hard for $EXPSPACE$ and $A$ $``$diagonalizes$"$ against all possible auto-reductions \cite{BU00}.
